---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(cairobasic)
set.seed(2)
```

# cairobasic

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![R build status](https://github.com/coolbutuseless/cairobasic/workflows/R-CMD-check/badge.svg)](https://github.com/coolbutuseless/cairobasic/actions)
<!-- badges: end -->

`cairobasic` is a package which provides a fast canvas for drawing operations.

This is a really demonstration package showing how [cairocore](http://github.com/coolbutuseless/cairocore)
may be made more palatable for programming within R.

This package currently only offers some basic drawing tools, but could easily
be forked/expanded to suit different needs.  

To get the most out of CairoGraphics at this stage, 
you would still need to use `cairocore`, but `cairobasic` will accumulate 
features based upon user feedback.


## Installation

You can install from [GitHub](https://github.com/coolbutuseless/cairobasic) with:

``` r
# install.package('remotes')
remotes::install_github('coolbutuseless/cairobasic')
```

## Using `cairobasic`

The `cairobasic` package provides an [R6](https://cran.r-project.org/package=R6)
class (`CairoBasic`) which keeps track of context information for rendering and
the actual rendering surface.

```{r example}
library(cairobasic)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a new 'CairoBasic' object
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
width  <- 800
height <- 400
cb     <- CairoBasic$new(width = width, height = height)


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add concentric circles
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
N <- 10
cb$add_circles(
  x    = rep(width/2, N),
  y    = 0,
  r    = seq(width, 0, length.out = N),
  fill = '#80808020'
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add Lines with rainbow colouring
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
N <- 500
cb$add_line_segments(
  x1 = rep(width/2, N),
  y1 = 0,
  x2 = seq(1, width, length.out = N),
  y2 = height,
  colour = rainbow(N, alpha = 0.1)
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add rectangles
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
N <- 10

xy <- expand.grid(x = seq(1, width/2, width/32), y = seq(1, height, width/32))
xy <- subset(xy, y < width/2 - x - width/16)

cb$add_rectangles(
  x      = xy$x,
  y      = xy$y,
  width  = width/32,
  height = width/32,
  fill   = terrain.colors(nrow(xy)),
  colour = '#20202020'
)


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add polygons
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cx  <- width  * 0.85
cy  <- height * 0.35
ang <- seq(0, 2*pi, pi/3)

x1  <- cx + 50 * sin(ang)
y1  <- cy + 50 * cos(ang)

x2  <- cx + 60 * sin(ang)
y2  <- cy + 60 * cos(ang)

x   <- c(x1, x2)
y   <- c(y1, y2)
idx <- as.integer(c(1, 1, 1, 1, 1, 1, 1,   2, 2, 2, 2, 2, 2, 2))

cb$add_polygons(
  x, y, idx, fill = NA, 
  linewidth = 5,
  colour = c('red', 'blue'))


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add Text
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cb$add_text("{cairobasic}", width*0.65 + 1, 10, fontsize = 50, colour = 'white')
cb$add_text("{cairobasic}", width*0.65    , 11, fontsize = 50, colour = '#606060a0')


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Show it
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cb$show(interpolate = TRUE)
```


```{r eval=FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Save to PNG
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cb$write_png("output.png")
```


## Working with `cairocore`

Read the [cairocore](https://github.com/coolbutuseless/cairocore) README for more information

```{r}
library(cairocore)

cairo_set_source_rgba(cb$cr, 1, 0, 0, 0.3)
cairo_set_line_width(cb$cr, 10)
cairo_set_dash(cb$cr, c(10, 15, 25), 3, 0)
cairo_rectangle(cb$cr, 100, 100, width-200, height-200)
cairo_stroke(cb$cr)

cb$show()
```




## Acknowledgements

* R Core for developing and maintaining the language.
* CRAN maintainers, for patiently shepherding packages onto CRAN and maintaining
the repository
